%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
        {\textbf{A Project of Deep Neural Networks Course}}{}
        \resumeItemListStart
        \resumeItem{Implementing Segnet neural network for \textbf{Semantic Segmentaion}}
        \resumeItem{Using \underline{pytorch} framework to implement the model.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{A project of Deep Neural Networks course}}{}
        \resumeItemListStart
        \resumeItem{Using \underline{Resnet18} and \underline{LSTM} model in an image captioning application with pytorch framework.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{A project of Deep Neural Networks course}}{}
        \resumeItemListStart
        \resumeItem{Implenting encoder section of a \textbf{transformer} network and use it for a translation application.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Iran's National Elites Foundation}}{Oct. 2022 - Oct. 2023}
        \resumeItemListStart
        \resumeItem{The project was to find a trajectory in a big searching space for an aircraft.}
        \resumeItem{There was lots of limitations to fly and surveillance devices that would have been avoided.}
        \resumeItem{Used a \underline{Graph} based search in the space to accomplish the task.}
        \resumeItem{\textbf{Highlights}: networkx, A*, DP, RCS, docker, flask, REST}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{final project of Advanced robotic course}}{}
        \resumeItemListStart
        \resumeItem{Localizing Anki robot in \textbf{Gazebo} using \textbf{particle filter} and \textbf{EKF}}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{an academic project}}{Feb. 2021 - Aug. 2021}
        \resumeItemListStart
        \resumeItem{Our project was to use \textbf{EEG signals} to play a simple video game}
        \resumeItem{My task was to implement an Adaptive neuro fuzzy inference system (\textbf{ANFIS}) algorithm due to the classification task}
        \resumeItem{\textbf{Supervisor} : \href{https://ece.ut.ac.ir/en/~dehaqani}{Dr. Mohammadreza Abolghasemi Dehaqani}}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{An Academic project}}{Sep 2021}
        \resumeItemListStart
        \resumeItem{Make a gym environment for simulating the results alongside a deep RL agent (\textbf{A3C}) to set each station's power some how reduce their conflict while maximizing the coverage area.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{final project of Reinforcement Learning course}}{}
        \resumeItemListStart
        \resumeItem{Implementing a \textbf{Deep Q network} architecture to trade on historical data of \href{http://www.tsetmc.com/}{Tehran Stock Exchange}}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{final project of Instrumentation course}}{}
        \resumeItemListStart
        \resumeItem{Predicting accurate values of acceleration, velocity and position using GPS and Accelometer.}
        \resumeItem{Used \textbf{Arduino DUE} to collect the data and implementing Kalman filter}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{A project in Big Data Course}}{}
        \resumeItemListStart
        \resumeItem{Our aim was to extract data from the \href{https://splus.ir/}{Soroush app} for analysis and dashboard creation using \underline{big data} methods.}
        \resumeItem{Personally responsible for web \underline{crawling} Soroush messenger data utilizing \textbf{Selenium} and establishing data transmission through \textbf{Kafka}. This crucial component ensured data flow to downstream project segments.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{A freelance project in \href{https://ponisha.ir/}{Ponisha}}}{Nov. 2020}
        \resumeItemListStart
        \resumeItem{Finding a dataset about surgical results and analyzing the results of surgeries for certain medical centers and patients}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{final project of social network course}}{May 2020}
        \resumeItemListStart
        \resumeItem{Our team was supposed to find customer's opinion about a product using the product's comments}
        \resumeItem{I crawled Digikala website using \textbf{Selenium} and implemented a simple sentiment analysis on the comments to make a KPI for each product}
        \resumeItem{\href{https://github.com/rezakarbasi/Digikala-Spider}{Link to the crawler repository}}
        \resumeItemListEnd


    % \resumeProjectHeading
        % {\textbf{Filters and Fractals} $|$ \emph{\href{https://github.com/arasgungore/filters-and-fractals}{\color{blue}GitHub}}}{}
          % \resumeItemListStart
            % \resumeItem{A C project which implements a variety of image processing operations that manipulate the size, filter, brightness, contrast, saturation, and other properties of PPM images from scratch.}
            % \resumeItem{Added recursive fractal generation functions to model popular fractals including Mandelbrot set, Julia set, Koch curve, Barnsley fern, and Sierpinski triangle in PPM format.}
          % \resumeItemListEnd
      
      % \resumeProjectHeading
        % {\textbf{Chess Bot} $|$ \emph{\href{https://github.com/arasgungore/chess-bot}{\color{blue}GitHub}}}{}
          % \resumeItemListStart
            % \resumeItem{A C++ project in which you can play chess against an AI with a specified decision tree depth that uses alpha-beta pruning algorithm to predict the optimal move.}
            % \resumeItem{Aside from basic moves, this mini chess engine also implements chess rules such as castling, en passant, fifty-move rule, threefold repetition, and pawn promotion.}
          % \resumeItemListEnd
      
      % \resumeProjectHeading
        % {\textbf{CMPE 250 Projects} $|$ \emph{\href{https://github.com/arasgungore/CMPE250-projects}{\color{blue}GitHub}}}{}
          % \resumeItemListStart
            % \resumeItem{Five Java projects assigned for the Data Structures and Algorithms (CMPE 250) course in the Fall 2021-22 semester.}
            % \resumeItem{These projects apply DS\&A concepts such as discrete-event simulation (DES) using priority queues, Dijkstra's shortest path algorithm, Prim's algorithm to find the minimum spanning tree (MST), Dinic's algorithm for maximum flow problems, and weighted job scheduling with dynamic programming to real-world problems.}
          % \resumeItemListEnd
      
    \resumeSubHeadingListEnd
